Stressing Bank Profitability for Interest Rate Risk

### 2013-09-05 LATEX/slides/nim.slides.tex
Fixed typo
Workplan explaining Rossi et al (2013) and PLS paper Slides in progress for Atlanta

\begin{frame}
\frametitle{Why study NIMs, continued}
\begin{itemize}
\item \vspace{0.0in} A few other banking crises have also been associated with depressed or negative NIMs; including,
\begin{itemize}
\item \vspace{0.125in} The Nordic banking crises (in Finland, Sweden, and Norway) of the late 1980s/early 1990s; and,
\item \vspace{0.125in} The U.K. secondary banking of 1973-75.
\end{itemize}
\item \vspace{0.25in} NII is an important part of bank profitability.
\begin{itemize}
\item \vspace{0.125in} Bank equity analysts direct considerable attention to NII and NIMs in evaluating future bank profitability.
\item \vspace{0.125in} This reflects the fact that NII and NIMs are less volatile than other components of bank revenue.
\end{itemize}
\end{itemize}
\end{frame}

>>>>

\begin{frame}
\frametitle{Why study NIMs, continued}
\begin{itemize}
\item \vspace{0.0in} A few other banking crises have also been associated with depressed or negative NIMs; including,
\begin{itemize}
\item \vspace{0.075in} The Nordic banking crises (in Finland, Sweden, and Norway) of the late 1980s/early 1990s; and,
\item \vspace{0.075in} The U.K. secondary banking of 1973-75.
\end{itemize}
\item \vspace{0.25in} NII is an important part of bank profitability.
\begin{itemize}
\item \vspace{0.075in} Bank equity analysts direct considerable attention to NII and NIMs in evaluating future bank profitability.
\item \vspace{0.075in} Interest earning assets account for about 85~percent of total assets.
\item \vspace{0.075in} NII and NIMs are less volatile than other components of bank revenue.
\end{itemize}
\end{itemize}
\end{frame}
